---
title: "a3_task4_leonardo_feitosa"
author: "Leonardo Feitosa"
date: "02/11/2020"
output: html_document
---

```{r setup, include=FALSE, message = FALSE, warning = FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(here)
library(janitor)
library(lubridate)
library(kableExtra)
```

## Read in urchins data

Here, I'll read in the urchins data

```{r, message = FALSE, warning = FALSE}
urchins <- read_csv(here("data","urchins.csv")) %>% 
  clean_names()
```

## Data wrangling

Here, I'll work on wrangling the data

- First, I'll create two new columns in the data set for year and month
- Second, I'll check if the dates are in Date format
- Third, I'll filter the data by common name (Purple Urchins), year (2010), month (January), and site (NAPL = Naples Reef)

```{r, message = FALSE, warning = FALSE}
urchins_clean <- urchins %>% 
  mutate(date_new = mdy(date)) %>% 
  mutate(year_new = year(date_new)) %>% 
  mutate(month_new = month(date_new))

class(urchins_clean$date_new)


purple_urchins <- urchins_clean %>% 
  filter(common_name == "Purple Urchin",
         year_new == "2010",
         month_new == "1",
         site == "NAPL")
```

## Observe distribution patterns for both treatments

First graph with exploratory analysis on data distribution

```{r, message = FALSE, warning = FALSE}
ggplot(purple_urchins, aes(x = size)) +
  geom_histogram() +
  facet_wrap(~ treatment)
```
#QQ plot

Second graph with exploratory analysis about data distribution

```{r, message = FALSE, warning = FALSE}
ggplot(purple_urchins, aes(sample = size)) +
  geom_qq() +
  facet_wrap(~ treatment)
```

- Both control and annual treatments seem to follow a normal distribution. However, this is not to say that they completely follow a normal distribution, as seen especially in the second graph (Q-Q plot) with the tails on both ends being somewhat out of the general diagonal. 

## Descriptive statistics table

Here, I'll create a table with descriptive statistics including means, starndard deviations (SD), and sample size. I'll use the kable() function from the `kableExtra` package to make a nicer looking table.

```{r, message = FALSE, warning = FALSE}
urchins_table <- purple_urchins %>% 
  group_by(treatment) %>% 
  summarise(mean = mean(size),
            sd = sd(size),
            median = median(size),
            n = n())

urchins_table %>% 
  kable(col.names = c("Treatment",
                      "Mean",
                      "SD",
                      "Median",
                      "N")) %>% 
  kable_styling(full_width = F)
```

## Two sample t.test

Here, I'll pull data for each factor from the treatment variable into vectors. Then, I'll use the t.test() function to calculate a two sample t-test between control and annual treatments. 

```{r, message = FALSE, warning = FALSE}
control_sample <- purple_urchins %>% 
  filter(treatment == "CONTROL") %>% 
  pull(size)

annual_sample <- purple_urchins %>% 
  filter(treatment == "ANNUAL") %>% 
  pull(size)

t.test(x = control_sample, annual_sample)
```


In the t-test results above, we can see that the means for each treatment tested are quite similar (~ 3.726 for the control and ~ 3.916 for the annual treatment). This is also seen in the SD values, which are very similar for both treatments with an almost equal sample size for each. Indeed, this is corroborated by the p value = 0.2536, which means that there is a ~25% chance that this similarity is not random. Since this percentage is considered pretty high, I accept my null hypothesis that there are no differences between populations and, thus the data obtained likely came from the same population. 













