---
title: "a3_task4_leonardo_feitosa"
author: "Leonardo Feitosa"
date: "02/11/2020"
output: html_document
---

```{r setup, include=FALSE, message = FALSE, warning = FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(here)
library(janitor)
library(lubridate)
library(kableExtra)
```

## Read in urchins data

```{r, message = FALSE, warning = FALSE}
urchins <- read_csv(here("data","urchins.csv")) %>% 
  clean_names()
```

## Data wrangling

```{r, message = FALSE, warning = FALSE}
urchins_clean <- urchins %>% 
  mutate(date_new = mdy(date)) %>% 
  mutate(year_new = year(date_new)) %>% 
  mutate(month_new = month(date_new))

class(urchins_clean$date_new)


purple_urchins <- urchins_clean %>% 
  filter(common_name == "Purple Urchin",
         year_new == "2010",
         month_new == "1",
         site == "NAPL")
```

## Observe distribution patterns for both treatments

First graph with exploratory analysis about data distribution

```{r, message = FALSE, warning = FALSE}
ggplot(purple_urchins, aes(x = size)) +
  geom_histogram() +
  facet_wrap(~ treatment)
```
#QQ plot

Second graph with exploratory analysis about data distribution

```{r, message = FALSE, warning = FALSE}
ggplot(purple_urchins, aes(sample = size)) +
  geom_qq() +
  facet_wrap(~ treatment)
```

- Both control and annual treatments seem to follow a normal distribution. However, this is not to say that they completely follow a normal distribution, as seen especially in the second graph (Q-Q plot) with the tails on both ends being somewhat out of the general axis. 

## Descriptive statistics table

```{r, message = FALSE, warning = FALSE}
urchins_table <- purple_urchins %>% 
  group_by(treatment) %>% 
  summarise(mean = mean(size),
            sd = sd(size),
            median = median(size),
            n = n())

urchins_table %>% 
  kable(col.names = c("Treatment",
                      "Mean",
                      "SD",
                      "Median",
                      "N")) %>% 
  kable_styling(full_width = F)
```

## Two sample t.test

```{r, message = FALSE, warning = FALSE}
control_sample <- purple_urchins %>% 
  filter(treatment == "CONTROL") %>% 
  pull(size)

annual_sample <- purple_urchins %>% 
  filter(treatment == "ANNUAL") %>% 
  pull(size)

t.test(x = control_sample, annual_sample)
```


In the t-test results above, we can see that the means for each treatment tested are quite similar (~ 3.726 for the control and ~ 3.916 for the annual treatment). Indeed, the p value of 0.2536 provides further evidence that there is a ~25% chance that this similarity is not random. Given the confidence interval, 













