---
title: "a3_task3_leonardo_feitosa"
author: "Leonardo Feitosa"
date: "30/10/2020"
output: html_document
---

```{r setup, include=FALSE, warning = FALSE, message = FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(here)
library(janitor)
library(lubridate)
library(kableExtra)
```

## Read in the data

Here, I'll read in the urchins data.

```{r, warning = FALSE, message = FALSE}
urchins <- read_csv(here("data","urchins.csv")) %>% 
  clean_names()
```

### Section 1

Here, I'll make the plots for exploratory data analysis.

- Boxplot

```{r, warning = FALSE, message = FALSE}
ggplot(urchins, aes(x = common_name, y = size)) +
  geom_boxplot() +
  labs(x = "Common name",
       y = "Size") +
  theme_bw()
```


- Histogram

```{r, warning = FALSE, message = FALSE}
ggplot(urchins, aes(x = size)) +
  geom_histogram()+
  facet_wrap(~ common_name) +
  labs(x = "Size",
       y = "") +
  theme_bw()
```

2 - Descriptive statistics table

Here, I'll make a descriptive table for the summary statistics with mean, standard deviation (SD), and sample size (n).

```{r, warning = FALSE, message = FALSE}
urchins_table <- urchins %>% 
  group_by(common_name) %>% 
  summarise(mean = mean(size),
            sd = sd(size),
            n = n())

urchins_table %>% 
  kable(col.names = c("Common name",
                      "Mean",
                      "SD",
                      "N")) %>% 
  kable_styling(full_width = F)
```

3 - Purple urchins have a mean of 4.469 while red urchins mean size is 6.776. Despite the lowest sample size, the red urchin samples have a higher spread (SD = 1.891) than purple (SD = 1.175), which means that red urchins have a less steep distribution than the purple urchins.


### Section 2

-1 Data wrangling

Here, I'll do some data wrangling to change the date variable from a character to an actual date. I'll also create a subset of the data for purple urchins and substitute acronyms for the sites for their complete names.

```{r, warning = FALSE, message = FALSE}
urchins_clean <- urchins %>% 
  mutate(date_new = mdy(date)) %>% 
  mutate(year_new = year(date_new))

class(urchins_clean$date_new)


purple_urchins <- urchins_clean %>% 
  filter(common_name == "Purple Urchin") %>% 
  mutate(site_full = case_when(
    site %in% c("NAPL") ~ "Naples Reef",
    site %in% c("AQUE") ~ "Arroyo Quemado Reef",
    site %in% c("CARP") ~ "Carpinteria Reef",
    site %in% c("MOHK") ~ "Mohawk Reef",
    site %in% c("IVEE") ~ "Isla Vista Reef"
  ))  
```

2 - Count data

Here, I'll make a table with count the number of observations for each year and site

```{r, warning = FALSE, message = FALSE}
purple_urchins %>% 
  select("year_new", "site_full") %>% 
  count(site_full, year_new)
```

3 - Exploratory graph

Here, I'll make a facet exploratory plot for each site between 2008 and 2020 with the purple urchins data set.

```{r, warning = FALSE, message = FALSE}
ggplot(purple_urchins, aes(x = year_new, fill = site_full)) +
  geom_bar(color = "black") +
  facet_wrap(~ site_full) +
  labs(x = "Year",
       y = "Number of individuals",
       title = "Purple urchin counts for five reefs (2008-2020)") +
  theme_bw() +
  theme(legend.position = "none")
```






















